Characterizing Exposure to and Sharing Knowledge of Drivers of Environmental Change in the St. Lawrence System in Canada

### 2020-06-02 Beauchesne-eDriversMS-SI.Rmd
update figures and add latest versions of manuscript in main folder (to update again)

---
title: Supplementary Material
fontsize: 12pt
output:
  pdf_document:
    toc: false
    number_sections: true
    keep_tex: true
  html_document:
    number_sections: true
header-includes:
    - \usepackage{float}
    - \usepackage{setspace}
    - \onehalfspacing
    - \usepackage[svgnames]{xcolor}
    - \usepackage[normalem]{ulem}
    - \definecolor{blue}{HTML}{20cad5}
relativeurls: true
bibliography: Beauchesne-eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

<!--
rmarkdown::render('./Revisions2/Beauchesne-eDriversMS-SI.rmd')
-->

@@

```{r tableS1, echo=F, fontsize=4}
load('../tables/tableS1.RData')
tableS1
```

@@

As in @halpern2008a and @halpern2015, we used the sum of coastal populations as
a proxy of direct human impact. We used Statistics Canada dissemination area
population count from the 2016 census to obtain coastal population size
around the St. Lawrence [@statistics-canada2017]. Dissemination areas are the smallest
standard geographic area in which census data are disseminated. They combine
to cover all of Canada and are highly variable in shapes and sizes.
\textcolor{blue}{For example, their sizes range from 0.0003 to over 44000 $km^2$ in our study area.}
The census provides population count within the boundary
of each dissemination area, which we used to evaluate total coastal population.

@@

\begin{figure}[H]
\centering
\includegraphics{./FigureS1.png}
\caption{Frequency distribution of the untransformed data for all driver layers.}
\label{hist}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{./FigureS2.png}
\caption{Distribution and intensity of transformed and normalized drivers in the Estuary and Gulf of St. Lawrence available on *eDrivers*.}
\label{drivers}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./FigureS3.png}
\caption{Frequency distribution of cumulative exposure (\textit{i.e.} sum of normalized driver intensity in each grid cell) and percent contribution of each driver to the frequency distribution of cumulative exposure in the Estuary and Gulf of St. Lawrence.}
\label{marimekko}
\end{figure}

# ~~Threat complexes~~ \textcolor{blue}{Cumulative exposure profiles}

@@

\begin{figure}[H]
\centering
\includegraphics{./FigureS4.png}
\caption{Validation procedure for the \textit{k-medoids} and \textit{k-means} clustering algorithms based on the number of cluster that maximizes average silhouette width (upper panels; Kaufman and Rousseeuw, 1990) and minimizes the total within-cluster sum of squares (WSS; lower panels).}
\label{valid}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./FigureS5.png}
\caption{Evaluation of inter-cluster dissimilarity using a similarity percentage analysis (SIMPER) with Manhattan distance (Clarke, 1993). The figure diagonal presents the distribution of the 6 clusters identified using the \textit{k-medoids} clustering algorithm. The lower triangle shows all combinations of inter-cluster dissimilarity with circular barplots showing the percent contribution to total dissimilarity of each driver and with the total inter-cluster dissimilarity in the center of the barplots. The upper triangle shows the average relative intensity of each driver for all driver combinations, with barplots to the left and the right representing the row and columns clusters, respectively.}
\label{inter}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./FigureS6.png}
\caption{Evaluation of intra-cluster similarity using the Manhattan distance transformed to a similarity index. The distribution of the 6 clusters is presented along with circular barplots showing the percent contribution to total similarity of each driver and with the total intra-cluster similarity in the center of the barplots.}
\label{intra}
\end{figure}

>>>>

---
title: Supplementary Material
fontsize: 12pt
output:
  pdf_document:
    toc: false
    number_sections: true
    keep_tex: true
  html_document:
    number_sections: true
header-includes:
    - \usepackage{float}
    - \usepackage{setspace}
    - \onehalfspacing
relativeurls: true
bibliography: Beauchesne-eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

<!--
rmarkdown::render('./Beauchesne-eDriversMS-SI.rmd')
-->

@@

```{r tableS1, echo=F, fontsize=4}
load('./tables/tableS1.RData')
tableS1
```

@@

As in @halpern2008a and @halpern2015, we used the sum of coastal populations as
a proxy of direct human impact. We used Statistics Canada dissemination area
population count from the 2016 census to obtain coastal population size
around the St. Lawrence [@statistics-canada2017]. Dissemination areas are the smallest
standard geographic area in which census data are disseminated. They combine
to cover all of Canada and are highly variable in shapes and sizes.
For example, their sizes range from 0.0003 to over 44000 $km^2$ in our study area.
The census provides population count within the boundary
of each dissemination area, which we used to evaluate total coastal population.

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/histograms.jpg}
\caption{Frequency distribution of the untransformed data for all driver layers.}
\label{hist}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{./Figures/drivers.jpg}
\caption{Distribution and intensity of transformed and normalized drivers in the Estuary and Gulf of St. Lawrence available on *eDrivers*.}
\label{drivers}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/marimekko.jpg}
\caption{Frequency distribution of cumulative exposure (\textit{i.e.} sum of normalized driver intensity in each grid cell) and percent contribution of each driver to the frequency distribution of cumulative exposure in the Estuary and Gulf of St. Lawrence.}
\label{marimekko}
\end{figure}

# Cumulative exposure profiles

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/validation.jpg}
\caption{Validation procedure for the \textit{k-medoids} and \textit{k-means} clustering algorithms based on the number of cluster that maximizes average silhouette width (upper panels; Kaufman and Rousseeuw, 1990) and minimizes the total within-cluster sum of squares (WSS; lower panels).}
\label{valid}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/interDissimilarity.jpg}
\caption{Evaluation of inter-cluster dissimilarity using a similarity percentage analysis (SIMPER) with Manhattan distance (Clarke, 1993). The figure diagonal presents the distribution of the 6 clusters identified using the \textit{k-medoids} clustering algorithm. The lower triangle shows all combinations of inter-cluster dissimilarity with circular barplots showing the percent contribution to total dissimilarity of each driver and with the total inter-cluster dissimilarity in the center of the barplots. The upper triangle shows the average relative intensity of each driver for all driver combinations, with barplots to the left and the right representing the row and columns clusters, respectively.}
\label{inter}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/intraSimilarity.jpg}
\caption{Evaluation of intra-cluster similarity using the Manhattan distance transformed to a similarity index. The distribution of the 6 clusters is presented along with circular barplots showing the percent contribution to total similarity of each driver and with the total intra-cluster similarity in the center of the barplots.}
\label{intra}
\end{figure}

### 2020-06-02 Beauchesne-eDriversMS.Rmd
update figures and add latest versions of manuscript in main folder (to update again)

<!--
rmarkdown::render('./Revisions2/Beauchesne-eDriversMS.Rmd', 'pdf_document')
-->

@@

\begin{figure}[H]
\centering
\includegraphics{./Figure1.jpg}
\caption{\sout{Description of the Estuary and Gulf of St. Lawrence in Eastern Canada.}\textcolor{blue}{Description of the St. Lawrence System in Eastern Canada, composed of the St. Lawrence Estuary and the Gulf of St. Lawrence. The Estuary is defined by the limit of seawater intrusion, close to Îles d'Orléans, to the west and by its connection to the Gulf near Pointe-des-Monts. The Gulf is an interior sea connected to the Atlantic by Cabot Strait and the Strait of Belle Isle to the south and north of Newfoundland, respectively.}}
\label{egsl}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figure2.jpg}
\caption{\textcolor{blue}{Simplified 2-driver example of driver co-occurrence between hypoxia and demersal destructive fisheries in the St. Lawrence}. An index of hypoxia ($A$) was created using bottom-water dissolved oxygen between 2013 and 2017 (Blais et al., 2018). Demersal destructive fisheries ($i.e.$ trawl and dredges) ($B$) intensity was evaluated from fisheries catch data collected between 2010 and 2015 used to measure annual area weighted total biomass ($kg$) in i $km^2$ grid cells (DFO, 2016b). See supplementary materials for more information on specific methodologies. Relative hypoxic stress and demersal destructive fisheries intensity was summed ($C$) to visualize their combined spatial distribution and intensity. Finally, individual density and the co-intensity of hypoxia and demersal destructive fisheries was investigated with a two-dimensional kernel analysis ($D$).}
\label{kernel}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figure5.jpg}
\caption{Distribution of \sout{threat complexes}\textcolor{blue}{areas with similar cumlative exposure profiles} in the Estuary and Gulf of St. Lawrence\textcolor{blue}{, identified through a clustering approach} (upper panel).  Mean intensity of all coastal (red), climate (green), fisheries (blue) and marine traffic (purple) drivers within each \sout{threat complex}\textcolor{blue}{cluster} (lower panel). Refer to Table 1 for acronym meaning and to the Supplementary Materials for more details.}
\label{cluster}
\end{figure}

@@

Table 1. List of drivers ~~currently~~ available on *eDrivers* and used for the analyses presented in this paper. Further details on methods and data are available in the Supplementary Material.

>>>>

<!--
rmarkdown::render('./Beauchesne-eDriversMS.Rmd', 'pdf_document')
-->

@@

\begin{figure}[H]
\centering
\includegraphics{./Figure1.jpg}
\caption{Description of the St. Lawrence System in Eastern Canada, composed of the St. Lawrence Estuary and the Gulf of St. Lawrence. The Estuary is defined by the limit of seawater intrusion, close to Île d'Orléans, to the west and by its connection to the Gulf near Pointe-des-Monts. The Gulf is an interior sea connected to the Atlantic by Cabot Strait and the Strait of Belle Isle to the south and north of Newfoundland, respectively.}
\label{egsl}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figure2.jpg}
\caption{\textcolor{blue}{Simplified 2-driver example of driver co-occurrence between hypoxia and demersal destructive fisheries in the St. Lawrence}. An index of hypoxia ($A$) was created using bottom-water dissolved oxygen between 2013 and 2017 (Blais et al., 2018). Demersal destructive fisheries ($i.e.$ trawl and dredges) ($B$) intensity was evaluated from fisheries catch data collected between 2010 and 2015 used to measure annual area weighted total biomass ($kg$) in 1 $km^2$ grid cells (DFO, 2016b). See supplementary materials for more information on specific methodologies. Relative hypoxic stress and demersal destructive fisheries intensity was summed ($C$) to visualize their combined spatial distribution and intensity. Finally, individual density and the co-intensity of hypoxia and demersal destructive fisheries was investigated with a two-dimensional kernel analysis ($D$).}
\label{kernel}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figure5.jpg}
\caption{Distribution of areas with similar cumulative exposure profiles in the Estuary and Gulf of St. Lawrence, identified through a clustering approach (Top). Mean intensity of all coastal (red), climate (green), fisheries (blue), and marine traffic (purple) drivers within each cluster (Bottom). Refer to Table 1 for acronym meaning and to the Supplementary Materials for more details.}
\label{cluster}
\end{figure}

@@

Table 1. List of drivers available on *eDrivers* and used for the analyses presented in this paper. Further details on methods and data are available in the Supplementary Materials.
